\documentclass[11pt]{article}
%Gummi|065|=)
\title{\textbf{AGT - Semestral work}}
\author{Teymur Azayev\\}
\date{}
\begin{document}

\maketitle


\section{Abstract}
In this document we will anylize some situations and decisions
that a fictional character named Kaiji is faced in an animated series called 'Ultimate survivor Kaiji'.  
This work is mostly aimed at placing the reader in the situation that our character faces and to provide some
game-theoretic analysis of some of the 'games' that happen throughout the series. 

\section{Introduction}
The story is as follows: Kaiji, along with 29 other gamblers are manipulated and forced to play a gambling game 
to pay off their very high debts to the Yakuza clan in Japan. The players are promised (and given the opportunity) that they can cancel all their debts and even turn a profit all in the course of one night, a typical gambler's hope. If a gambler loses then he is executed or forced to work as a slave in underground mines for years. The event takes place in a cruiser ship and serves as entertainment for the very rich people who observe these players through cameras and one-way windows. There are many events that happen throughout the course of the series but most
are too complex or out of the scope of this work so we will only take a look at a few events and games, sometimes
only considering a simplified version.

\section{Game setting}
The first two games that we will take a look at have the following setting: 
The 30 players are placed in the main playing hall where they each receive 3 stars and 12 cards. 
The game that they will be playing is basically a Rock, Scissors and Paper game, but with a few twists.
There are 3 types of cards, each symbolizing 'Rock', 'Scissors' and 'Paper' (from now on R,S,P). Each player starts off with 4 of each. Each player can play with an opponent of their choosing by inviting them (the opponent is allowed to refuse) to go to one of the game tables supervised by a suit and play one or more games. A player bets one or more of his stars. A game consists of both players selecting a card, the 'Check' phase, then putting it on the table, the 'set' phase, and followed by opening the cards, the 'open' phase. The winner is decided by the traditional rules of the RSP game. After the game has been played, the played cards are discarded. There is a publicly available monitor which shows the current amount of each card left in circulation amongs the players. 
In the series this game is refered to as "Restricted Rock, Scissors, Paper" (RRSP).
Before the start of the games the players are all forced to borrow a sum of money in the range 1-20M yen whose interest compounds at an hourly rate.
The players have 4 hours to play. At the end of the time limit, anyone with less than 3 stars or having more than zero cards is considered to have lost and is dealt with as mentioned in the introduction. Anyone who did not lose can then decided what to do with their excess stars/money. The arena is monitored players are obviously not allowed to destroy or discard their cards. Besides some other obvious details there are no more rules to the game and players can manipulate/take advantage of anything they can at their will. \\

\section{Strategic overview}
The reader is now asked to imagine how they would play this game in such an extreme scenario and what their strategy would be. Obviously the goal is to get as many stars as possible (they can be sold for extremely high amounts to players with less than 3 stars at the end of the time limit) and to get rid of all the 12 cards as fast as possible. To remind the reader of the rules of the game:  Each player has 4 of each cards in their hand, 3 stars and their starting money. 

\section{Card elimination}
At the beginning of the game, Kaiji is approached by another man who offers him a deal. The deal is to cheat the game in the following way. They will play the game of RRSP against each other 12 times, each time matching their cards to discard them. This way they will quickly eliminate all 12 cards and leave the ship with all 3 stars each and live another day. We will now take a quick look at if such a deal is worth taking, and how we would play such a game considering that we are rational agents and that our opponent (ally) is rational as well and that he will not hesitate to betray us. 



\end{document}
